---
title: "Infection Risk Factors and Model Comparison"
author: "Andrew Azman and Stephen Lauer"
date: "15-Jan-2020"
output: 
  pdf_document: 
    keep_tex: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message = FALSE,error = FALSE,warning = FALSE)
knitr::opts_knit$set(root.dir = here::here())
```

## Some Setup

```{r preamble, include=FALSE}
library(pacman)
source("source/utils.R")
reload_source()
p_load(INLA,flextable,officer)
```

Let's add a little helper function for running some of the models:

```{r helper}
## define a few helper functions for later
##' helper for running inla models
##' @param formula1 
##' @param data 
##' @return 
run_inla_model<-function(formula1,my_data,my_spde){
    output <- inla(formula1,
                   data=inla.stack.data(my_data, spde=my_spde),
                   family=c("binomial"),
                   Ntrials=1,
                   control.predictor=list(A=inla.stack.A(my_data),compute=TRUE),
                   control.compute=list(dic=TRUE))
    return(output)
}

```

### Data

First, we will load data from the survey:

```{r data}
## load data for analyses
serosurvey_dat <- readRDS("generated_data/serosurvey-with-rf-preds.rds") %>% 
    left_join(readRDS("data/community-data.rds")) %>% 
    mutate(age_group=cut(age,c(0,4,14,100),labels = 1:3),
           pred_365 = ifelse(pred_365==TRUE,1,0) %>% as.numeric,
           pred_200 = ifelse(pred_200==TRUE,1,0),
           pred_100 = ifelse(pred_100==TRUE,1,0))
```

### Setting up SPDE 
First we need to set up our SPDE spatial mesh (`spde`) and the spatial indices (`s_index`). 

```{r spde}
hhl_locs_ll <- serosurvey_dat %>%
    select(lon,lat,hhid,community_id) %>% 
    st_as_sf(coords = c("lon","lat"),
             crs="+proj=longlat +datum=WGS84 +no_defs")

hhl_locs_btm <- hhl_locs_ll %>% transform_to_btm() %>% st_coordinates
serosurvey_dat$hhl_easting <- hhl_locs_btm[,"X"]
serosurvey_dat$hhl_northing <- hhl_locs_btm[,"Y"]

## MESH
## Build mesh around household coordinates 
bnd <- inla.nonconvex.hull(hhl_locs_btm,convex=-0.1) ## inla mesh segment

bgd0 <- load_bgd_shp(level=0) %>%
    transform_to_btm() 

#meshbuilder() ## shiny app
mesh <- inla.mesh.2d(boundary = bnd  ,
                     loc=hhl_locs_btm,
                     offset=c(-0.05, -0.05),
                     cutoff = 2000, ## if households are less than 2km apart, builds only a single vertex
                     max.edge=c(30000,50000))

## let's have a quick look at the mesh
plot(mesh,asp=1,main="hhl")
points(hhl_locs_btm[,"X"],hhl_locs_btm[,"Y"],pch=19,cex=0.5,col="orange")

## now make the SPDE model on the mesh
spde <- inla.spde2.matern(mesh=mesh, alpha=2) # alpha is Fractional operator order
s_index <- inla.spde.make.index(name="spatial.field",n.spde=spde$n.spde) 
```

Now let's build the main stack/scaffolding for the model. First we will restrict to observations we have complete data for.

```{r stack}
## we lose 17 that  we don't have
## serological predictions for and then
## another 12 are missing incomeSumm
dat_no_na_riskfactors <- serosurvey_dat %>%
    select("pred_365",
           "pred_200",
           "pred_100",
           "age_group",
           "sex",
           "elec",
           "ownerHH",
           "land",
           "educationSumm",
           "incomeSumm",
           "altitude",
           "travel",
           "logpop",
           "urban",
           "travel_time",
           "poverty",
           "distance_to_water",
           "community_id",
           "hhl_easting",
           "hhl_northing",
           "community_id","hhid"
    ) %>%
    mutate(educationSumm=relevel(educationSumm, "4"),
           age_group=relevel(age_group, "3"),
           incomeSumm=relevel(incomeSumm, "3")) %>% 
    na.omit

## observation/prediction matrix
A_est_multi <- inla.spde.make.A(mesh=mesh,
                                loc=dat_no_na_riskfactors %>%
                                    select(hhl_easting,hhl_northing) %>%
                                    as.matrix)

## first we need to create the stack data for estimation
model_matrix <- model.matrix(~age_group+sex+elec+travel+ownerHH+land+
                                 educationSumm+logpop+incomeSumm+altitude+
                                 poverty+urban+
                                 travel_time+poverty+distance_to_water,
                             dat_no_na_riskfactors)[, -1]

## creating a stack called "est"
stack_est_multi <- inla.stack(
    data=list(y=dat_no_na_riskfactors[,'pred_365'] %>% unlist), ## response
    A=list(A_est_multi, 1,1,1), ## projector matrix
    effects=list(s_index,
                 data.frame(Intercept=1,model_matrix), 
                 list(village.index=dat_no_na_riskfactors$community_id),
                 list(hh.index=dat_no_na_riskfactors$hhid)),
    tag="est")
```


## Univariate regresssion models using individual-level data 

Now let's run a bunch of univariate models for the random forest model
outcomes including village- and household-level random effects in
addtion to the Matern spatial covariance function:

```{r univariate individual, cache=TRUE}
set.seed(1)
formula_age <- y~-1+Intercept+age_group1+age_group2+
    f(village.index, model="iid")+
    f(hh.index, model="iid")+
    f(spatial.field, model=spde)
model_age <- run_inla_model(formula_age,stack_est_multi,my_spde=spde)

formula_altitude <- y~-1+Intercept+altitude+
    f(village.index, model="iid")+
    f(hh.index, model="iid")+
    f(spatial.field, model=spde)
model_altitude <- run_inla_model(formula_altitude,stack_est_multi,my_spde=spde)

formula_sex <- y~-1+Intercept+sexMale+
    f(village.index, model="iid")+
    f(hh.index, model="iid")+f(spatial.field, model=spde)
model_sex <- run_inla_model(formula_sex,stack_est_multi,my_spde=spde)

formula_elec <- y~-1+Intercept+elecTRUE+
    f(village.index, model="iid")+
    f(hh.index, model="iid")+
    f(spatial.field, model=spde)
model_elec <- run_inla_model(formula_elec,stack_est_multi,my_spde=spde)

formula_owner <- y~-1+Intercept+ownerHHTRUE+
    f(village.index, model="iid")+
    f(hh.index, model="iid")+
    f(spatial.field, model=spde)
model_owner <- run_inla_model(formula_owner,stack_est_multi,my_spde=spde)

formula_land <- y~-1+Intercept+landTRUE+
    f(village.index, model="iid")+
    f(hh.index, model="iid")+
    f(spatial.field, model=spde)
model_land <- run_inla_model(formula_land,stack_est_multi,my_spde=spde)

formula_edu <- y~-1+Intercept+educationSumm3+educationSumm2+educationSumm1+
    f(village.index, model="iid")+
    f(hh.index, model="iid")+
    f(spatial.field, model=spde)
model_edu <- run_inla_model(formula_edu,stack_est_multi,my_spde=spde)

formula_income <- y~-1+Intercept+incomeSumm2+incomeSumm1+incomeSumm4+
    f(village.index, model="iid")+
    f(hh.index, model="iid")+
    f(spatial.field, model=spde)
model_income <- run_inla_model(formula_income,stack_est_multi,my_spde=spde)

formula_travel <- y~-1+Intercept+travel1+travel2+travel3+
    f(village.index, model="iid")+
    f(hh.index, model="iid")+
    f(spatial.field, model=spde)
model_travel <- run_inla_model(formula_travel,stack_est_multi,my_spde=spde)

formula_pop <- y~-1+Intercept+logpop+
    f(village.index, model="iid")+f(hh.index, model="iid")+f(spatial.field, model=spde)
model_pop <- run_inla_model(formula_pop,stack_est_multi,my_spde=spde)

## urban based on census classifications
formula_urban <- y~-1+Intercept+urbanTRUE+
    f(village.index, model="iid")+f(hh.index, model="iid")+f(spatial.field, model=spde)
model_urban <- run_inla_model(formula_urban,stack_est_multi,my_spde=spde)

## how about an interaction tern with pop and urban?
formula_pop_cross_urban <- y~-1+Intercept+urbanTRUE+logpop+urbanTRUE:logpop+
    f(village.index, model="iid")+f(hh.index, model="iid")+f(spatial.field, model=spde)
model_pop_cross_urban <- run_inla_model(formula_pop_cross_urban,stack_est_multi,my_spde=spde)

## don't want to include friction and travel time as they are transformations of one another.
## chosing travel time due to interpretability and no real difference in niceness of dist
formula_travel_time <- y~-1+Intercept+travel_time+
    f(village.index, model="iid")+f(hh.index, model="iid")+f(spatial.field, model=spde)
model_travel_time <- run_inla_model(formula_travel_time,stack_est_multi,my_spde=spde)

formula_poverty <- y~-1+Intercept+poverty+
    f(village.index, model="iid")+f(hh.index, model="iid")+f(spatial.field, model=spde)
model_poverty <- run_inla_model(formula_poverty,stack_est_multi,my_spde=spde)

formula_water <- y~-1+Intercept+distance_to_water+
    f(village.index, model="iid")+f(hh.index, model="iid")+f(spatial.field, model=spde)
model_water <- run_inla_model(formula_water,stack_est_multi,my_spde=spde)

## now combine them all
coefs_mv_uni <-
    bind_rows(
        bind_cols(
            variable = rownames(model_urban$summary.fixed),
            sapply(model_urban$marginals.fixed,
                   function(x) exp(inla.hpdmarginal(p = .95, x))) %>%
                t %>% data.frame %>%
                magrittr::set_colnames(c("low","high")),
            median = exp(model_urban$summary.fixed$`0.5quant`),
            model = rep("univariate",nrow(model_urban$summary.fixed))) %>%
            filter(variable != "Intercept"),    
        bind_cols(
            variable = rownames(model_altitude$summary.fixed),
            sapply(model_altitude$marginals.fixed,
                   function(x) exp(inla.hpdmarginal(p = .95, x))) %>%
                t %>% data.frame %>%
                magrittr::set_colnames(c("low","high")),
            median = exp(model_altitude$summary.fixed$`0.5quant`),
            model = rep("univariate",nrow(model_altitude$summary.fixed))) %>%
            filter(variable != "Intercept"),    
        bind_cols(
            variable = rownames(model_water$summary.fixed),
            sapply(model_water$marginals.fixed,
                   function(x) exp(inla.hpdmarginal(p = .95, x))) %>%
                t %>% data.frame %>%
                magrittr::set_colnames(c("low","high")),
            median = exp(model_water$summary.fixed$`0.5quant`),
            model = rep("univariate",nrow(model_water$summary.fixed))) %>%
            filter(variable != "Intercept"),
        bind_cols(
            variable = rownames(model_poverty$summary.fixed),
            sapply(model_poverty$marginals.fixed,
                   function(x) exp(inla.hpdmarginal(p = .95, x))) %>%
                t %>% data.frame %>%
                magrittr::set_colnames(c("low","high")),
            median = exp(model_poverty$summary.fixed$`0.5quant`),
            model = rep("univariate",nrow(model_poverty$summary.fixed))) %>%
            filter(variable != "Intercept"),
        bind_cols(
            variable = rownames(model_travel_time$summary.fixed),
            sapply(model_travel_time$marginals.fixed,
                   function(x) exp(inla.hpdmarginal(p = .95, x))) %>%
                t %>% data.frame %>%
                magrittr::set_colnames(c("low","high")),
            median = exp(model_travel_time$summary.fixed$`0.5quant`),
            model = rep("univariate",
                        nrow(model_travel_time$summary.fixed))) %>%
            filter(variable != "Intercept"),
        bind_cols(
            variable = rownames(model_pop$summary.fixed),
            sapply(model_pop$marginals.fixed,
                   function(x) exp(inla.hpdmarginal(p = .95, x))) %>%
                t %>% data.frame %>%
                magrittr::set_colnames(c("low","high")),
            median = exp(model_pop$summary.fixed$`0.5quant`),
            model = rep("univariate",nrow(model_pop$summary.fixed))) %>%
            filter(variable != "Intercept"),
        bind_cols(
            variable = rownames(model_income$summary.fixed),
            sapply(model_income$marginals.fixed,
                   function(x) exp(inla.hpdmarginal(p = .95, x))) %>%
                t %>% data.frame %>%
                magrittr::set_colnames(c("low","high")),
            median = exp(model_income$summary.fixed$`0.5quant`),
            model = rep("univariate",nrow(model_income$summary.fixed))) %>%
            filter(variable != "Intercept"),
        bind_cols(
            variable = rownames(model_edu$summary.fixed),
            sapply(model_edu$marginals.fixed,
                   function(x) exp(inla.hpdmarginal(p = .95, x))) %>%
                t %>% data.frame %>%
                magrittr::set_colnames(c("low","high")),
            median = exp(model_edu$summary.fixed$`0.5quant`),
            model = rep("univariate",nrow(model_edu$summary.fixed))) %>%
            filter(variable != "Intercept"),
        bind_cols(
            variable = rownames(model_land$summary.fixed),
            sapply(model_land$marginals.fixed,
                   function(x) exp(inla.hpdmarginal(p = .95, x))) %>%
                t %>% data.frame %>%
                magrittr::set_colnames(c("low","high")),
            median = exp(model_land$summary.fixed$`0.5quant`),
            model = rep("univariate",nrow(model_land$summary.fixed))) %>%
            filter(variable != "Intercept"),
        bind_cols(
            variable = rownames(model_owner$summary.fixed),
            sapply(model_owner$marginals.fixed,
                   function(x) exp(inla.hpdmarginal(p = .95, x))) %>%
                t %>% data.frame %>%
                magrittr::set_colnames(c("low","high")),
            median = exp(model_owner$summary.fixed$`0.5quant`),
            model = rep("univariate",nrow(model_owner$summary.fixed))) %>%
            filter(variable != "Intercept"),
        bind_cols(
            variable = rownames(model_elec$summary.fixed),
            sapply(model_elec$marginals.fixed,
                   function(x) exp(inla.hpdmarginal(p = .95, x))) %>%
                t %>% data.frame %>%
                magrittr::set_colnames(c("low","high")),
            median = exp(model_elec$summary.fixed$`0.5quant`),
            model = rep("univariate",nrow(model_elec$summary.fixed))) %>%
            filter(variable != "Intercept"),
        bind_cols(
            variable = rownames(model_travel$summary.fixed),
            sapply(model_travel$marginals.fixed,
                   function(x) exp(inla.hpdmarginal(p = .95, x))) %>%
                t %>% data.frame %>%
                magrittr::set_colnames(c("low","high")),
            median = exp(model_travel$summary.fixed$`0.5quant`),
            model = rep("univariate",nrow(model_travel$summary.fixed))) %>%
            filter(variable != "Intercept"),
        bind_cols(
            variable = rownames(model_sex$summary.fixed),
            sapply(model_sex$marginals.fixed,
                   function(x) exp(inla.hpdmarginal(p = .95, x))) %>%
                t %>% data.frame %>%
                magrittr::set_colnames(c("low","high")),
            median = exp(model_sex$summary.fixed$`0.5quant`),
            model = rep("univariate",nrow(model_sex$summary.fixed))) %>%
            filter(variable != "Intercept"),
        bind_cols(
            variable = rownames(model_age$summary.fixed),
            sapply(model_age$marginals.fixed,
                   function(x) exp(inla.hpdmarginal(p = .95, x))) %>%
                t %>% data.frame %>%
                magrittr::set_colnames(c("low","high")),
            median = exp(model_age$summary.fixed$`0.5quant`),
            model = rep("univariate",nrow(model_age$summary.fixed))) %>%
            filter(variable != "Intercept")
    )

write_csv(coefs_mv_uni,"generated_data/univariate_rf.csv")
```

Quick look at the univariate analyses:

```{r univariate analysis}
# coefs_mv_uni <- read_csv(here("generated_data/univariate_rf.csv"))
kable(coefs_mv_uni)
```

## Multivariable regression of individual-level data

First for RF predicted outcomes. Note that I played with different
prior specifications for the random effects for village and
household. The verison with the loggamma prior seems to have the most
reasonable posterior precicsion for village and slightly better
CPO/WAIC (if this is even meaningful here).

```{r multivariate individual, cache=TRUE}
formula_all <- y~-1+Intercept+age_group1 + age_group2+
    sexMale+
    elecTRUE+ownerHHTRUE+landTRUE+urbanTRUE+
    incomeSumm2+incomeSumm1+incomeSumm4+
    educationSumm3+educationSumm2+educationSumm1+
    logpop+travel_time+poverty+
    travel1+travel2+travel3+
    distance_to_water+altitude+
    f(spatial.field, model=spde)+
    ## f(village.index, model="iid")+
    ## f(hh.index, model="iid")
    f(village.index, model="iid",prior="loggamma",param=c(0.1,1))+
    f(hh.index, model="iid",prior="loggamma",param=c(0.1,1))

formula_all_no_spde <- y~-1+Intercept+
    age_group1 + age_group2+
    sexMale+
    elecTRUE+ownerHHTRUE+landTRUE+urbanTRUE+
    incomeSumm2+incomeSumm1+incomeSumm4+
    educationSumm3+educationSumm2+educationSumm1+
    logpop+travel_time+poverty+
    travel1+travel2+travel3+distance_to_water+altitude+
    f(village.index, model="iid",prior="loggamma",param=c(0.1,1))+
    f(hh.index, model="iid",prior="loggamma",param=c(0.1,1))

formula_all_no_res <- y~-1+Intercept+
    age_group1 + age_group2+
    sexMale+
    elecTRUE+ownerHHTRUE+landTRUE+urbanTRUE+
    incomeSumm2+incomeSumm1+incomeSumm4+
    educationSumm3+educationSumm2+educationSumm1+
    logpop+travel_time+poverty+
    travel1+travel2+travel3+distance_to_water+altitude

formula_only_spde <- y~-1+Intercept+
    age_group1 + age_group2+
    sexMale+
    elecTRUE+ownerHHTRUE+landTRUE+urbanTRUE+
    incomeSumm2+incomeSumm1+incomeSumm4+
    educationSumm3+educationSumm2+educationSumm1+
    logpop+travel_time+poverty+
    travel1+travel2+travel3+distance_to_water+altitude+
    f(spatial.field, model=spde)

set.seed(1)
output_all <- inla(formula_all,
                   data=inla.stack.data(stack_est_multi, spde=spde),
                   family="binomial",
                   Ntrials=1,
                   control.inla=list(correct=TRUE,correct.factor=10),
                   control.predictor=list(A=inla.stack.A(stack_est_multi),
                                          compute=TRUE),
                   control.compute=list(dic=TRUE,waic=TRUE,cpo=TRUE),
                   control.fixed=list(expand.factor.strategy="model.matrix"))

#summary(output_all)

## same but without spatial effects
output_all_no_spde <- inla(
    formula_all_no_spde,
    data=inla.stack.data(stack_est_multi),
    family="binomial",
    Ntrials=1,
    control.inla=list(correct=TRUE,correct.factor=10),
    control.predictor=list(A=inla.stack.A(stack_est_multi),compute=TRUE),
    control.compute=list(dic=TRUE,waic=TRUE,cpo=TRUE),
    control.fixed=list(expand.factor.strategy="model.matrix"))

output_all_no_res <- inla(
    formula_all_no_res,
    data=inla.stack.data(stack_est_multi),
    family="binomial",
    Ntrials=1,
    control.inla=list(correct=TRUE,correct.factor=10),
    control.predictor=list(A=inla.stack.A(stack_est_multi),compute=TRUE),
    control.compute=list(dic=TRUE,waic=TRUE,cpo=TRUE),
    control.fixed=list(expand.factor.strategy="model.matrix"))

output_all_only_spde <- inla(
    formula_only_spde,
    data=inla.stack.data(stack_est_multi,spde=spde),
    family="binomial",
    Ntrials=1,
    control.inla=list(correct=TRUE,correct.factor=10),
    control.predictor=list(A=inla.stack.A(stack_est_multi),compute=TRUE),
    control.compute=list(dic=TRUE,waic=TRUE,cpo=TRUE),
    control.fixed=list(expand.factor.strategy="model.matrix"))
```

```{r extract inla est}
## Binding all risk factor coefficients
coefs_mv <-
    bind_rows(
        coefs_mv_uni,
        bind_cols(
            variable = rownames(output_all$summary.fixed),
            sapply(output_all$marginals.fixed,
                   function(x) exp(inla.hpdmarginal(p = .95, x))) %>%
                t %>% data.frame %>%
                magrittr::set_colnames(c("low","high")) ,
            median = exp(output_all$summary.fixed$`0.5quant`),
            model = rep("full model",22)) %>%
            filter(variable != "Intercept"),
        bind_cols(
            variable = rownames(output_all_no_spde$summary.fixed),
            sapply(output_all_no_spde$marginals.fixed,
                   function(x) exp(inla.hpdmarginal(p = .95, x))) %>%
                t %>% data.frame %>%
                magrittr::set_colnames(c("low","high")),
            median = exp(output_all_no_spde$summary.fixed$`0.5quant`),
            model = rep("no spatial \n random effects",22))  %>%
            filter(variable != "Intercept"),
        bind_cols(
            variable = rownames(output_all_only_spde$summary.fixed),
            sapply(output_all_only_spde$marginals.fixed,
                   function(x) exp(inla.hpdmarginal(p = .95, x))) %>%
                t %>% data.frame %>%
                magrittr::set_colnames(c("low","high")),
            median = exp(output_all_only_spde$summary.fixed$`0.5quant`),
            model = rep("only spatial \n random effects",22))  %>%
            filter(variable != "Intercept"),
        bind_cols(
            variable = rownames(output_all_no_res$summary.fixed),
            sapply(output_all_no_res$marginals.fixed,
                   function(x) exp(inla.hpdmarginal(p = .95, x))) %>%
                t %>% data.frame %>%
                magrittr::set_colnames(c("low","high")),
            median = exp(output_all_no_res$summary.fixed$`0.5quant`),
            model = rep("no random effects",22))  %>%
            filter(variable != "Intercept")) %>%
    mutate(variable = recode_risk_factors(variable))

write_csv(coefs_mv,"generated_data/covariate_ests.csv")
```

Now, let's make a plot for the supplement illustrating the effect size across models:

```{r effect size figures}
# coefs_mv <- read_csv(here("generated_data/covariate_ests.csv"))
coefs_mv %>%
    mutate(variable = factor(variable,levels=c(
        "0-4 years",
        "5-14 years",
        ">14 years",
        "male",
        "no travel in last 6 months",
        "travel last week",
        "travel last month",
        "travel last 6 months",
        "<7,000TK","7,000-9,999TK","10,000-20,000TK",">20,000TK",
        "no school (head hhl)","primary school (head hhl)","secondary school (head hhl)","post-secondary education (head hhl)",
        "electricity in house",
        "owns land",
        "owns home",
        "urban",
        "distance to major water body (per 10km)",
        "poverty index",
        "travel time to nearest city (min)",
        "altitude",
        "population density (log)"))) %>%
    ggplot(aes(y=median, x=variable, color=model)) +
    geom_point(alpha=.75,size=2,position=position_dodge(width=0.5)) +
    geom_errorbar(aes(ymin=low,ymax=high),
                  width=1,alpha=.5,position=position_dodge(width=0.5)) +
    geom_hline(yintercept=1,col="grey") + 
    coord_flip() +
    theme_minimal() +
    scale_y_log10("odds ratio", breaks=2^(-4:4)) +
    xlab("") +
    theme(legend.position = "bottom")

ggsave("figures/covariate_comp_plot.pdf",width=9,height=7)
ggsave("figures/covariate_comp_plot.png",width=9,height=7)
```

Now we will make Table 1 for the manuscript:
```{r effect table, eval=F}
## make a nicer table for publication
ft <- tibble(variable = c(
    "0-4 years",
    "5-14 years",
    ">14 years",
    "male",
    "no travel in last 6 months",
    "travel last week",
    "travel last month",
    "travel last 6 months",
    "<7,000TK","7,000-9,999TK","10,000-20,000TK",">20,000TK",
    "no school (head hhl)","primary school (head hhl)","secondary school (head hhl)","post-secondary education (head hhl)",
    "electricity in house",
    "owns land",
    "owns home",
    "urban",
    "distance to major water body (per 10km)",
    "poverty index",
    "travel time to nearest city (min)",
    "altitude",
    "population density (log)"),
    n = c(
        sprintf("%.0f (%.2f)",sum(dat_no_na_riskfactors$age_group==1),
                mean(dat_no_na_riskfactors$age_group==1)),
        sprintf("%.0f (%.2f)",sum(dat_no_na_riskfactors$age_group==2),
                mean(dat_no_na_riskfactors$age_group==2)),
        sprintf("%.0f (%.2f)",sum(dat_no_na_riskfactors$age_group==3),
                mean(dat_no_na_riskfactors$age_group==3)),
        sprintf("%.0f (%.2f)",sum(dat_no_na_riskfactors$sex=="Male"),
                mean(dat_no_na_riskfactors$sex=="Male")),
        sprintf("%.0f (%.2f)",sum(dat_no_na_riskfactors$travel==4),
                mean(dat_no_na_riskfactors$travel==4)),
        sprintf("%.0f (%.2f)",sum(dat_no_na_riskfactors$travel==1),
                mean(dat_no_na_riskfactors$travel==1)),
        sprintf("%.0f (%.2f)",sum(dat_no_na_riskfactors$travel==2),
                mean(dat_no_na_riskfactors$travel==2)),
        sprintf("%.0f (%.2f)",sum(dat_no_na_riskfactors$travel==3),
                mean(dat_no_na_riskfactors$travel==3)),
        sprintf("%.0f (%.2f)",sum(dat_no_na_riskfactors$incomeSumm == 1),
                mean(dat_no_na_riskfactors$incomeSumm==1)),
        sprintf("%.0f (%.2f)",sum(dat_no_na_riskfactors$incomeSumm == 2),
                mean(dat_no_na_riskfactors$incomeSumm==2)),
        sprintf("%.0f (%.2f)",sum(dat_no_na_riskfactors$incomeSumm == 3),
                mean(dat_no_na_riskfactors$incomeSumm==3)),
        sprintf("%.0f (%.2f)",sum(dat_no_na_riskfactors$incomeSumm == 4),
                mean(dat_no_na_riskfactors$incomeSumm==4)),
        sprintf("%.0f (%.2f)",sum(dat_no_na_riskfactors$educationSumm == 4),
                mean(dat_no_na_riskfactors$educationSumm==4)),
        sprintf("%.0f (%.2f)",sum(dat_no_na_riskfactors$educationSumm == 3),
                mean(dat_no_na_riskfactors$educationSumm==3)),
        sprintf("%.0f (%.2f)",sum(dat_no_na_riskfactors$educationSumm == 2),
                mean(dat_no_na_riskfactors$educationSumm==2)),
        sprintf("%.0f (%.2f)",sum(dat_no_na_riskfactors$educationSumm == 1),
                mean(dat_no_na_riskfactors$educationSumm==1)),
        sprintf("%.0f (%.2f)",sum(dat_no_na_riskfactors$elec==TRUE),
                mean(dat_no_na_riskfactors$elec==TRUE)),
        sprintf("%.0f (%.2f)",sum(dat_no_na_riskfactors$land==TRUE),
                mean(dat_no_na_riskfactors$land==TRUE)),
        sprintf("%.0f (%.2f)",sum(dat_no_na_riskfactors$ownerHH==TRUE),
                mean(dat_no_na_riskfactors$ownerHH==TRUE)),
        sprintf("%.0f (%.2f)",sum(dat_no_na_riskfactors$urban==TRUE),
                mean(dat_no_na_riskfactors$urban==TRUE)),
        sprintf("%.2f (%.2f)",mean(dat_no_na_riskfactors$distance_to_water),
                sd(dat_no_na_riskfactors$distance_to_water)),
        sprintf("%.2f (%.2f)",mean(dat_no_na_riskfactors$poverty),
                sd(dat_no_na_riskfactors$poverty)),               
        sprintf("%.2f (%.2f)",mean(dat_no_na_riskfactors$travel_time),
                sd(dat_no_na_riskfactors$travel_time)),  
        sprintf("%.2f (%.2f)",mean(dat_no_na_riskfactors$altitude),
                sd(dat_no_na_riskfactors$altitude)),  
        sprintf("%.2f (%.2f)",mean(dat_no_na_riskfactors$logpop),
                sd(dat_no_na_riskfactors$logpop)))) %>% 
    left_join(coefs_mv %>% 
                  filter(model %in% c("full model","univariate")) %>% 
                  mutate(est = sprintf("%.2f (%.2f-%.2f)",
                                       median,low,high)) %>% 
                  select(-low:-median) %>%
                  spread(model,est), by="variable") %>% 
    mutate(`full model` = ifelse(is.na(`full model`),"-",`full model`),
           univariate = ifelse(is.na(univariate),"-",univariate)) %>% 
    flextable() %>%
    autofit

read_docx() %>% 
    body_add_flextable(value = ft) %>% 
    print(target = "tables/table1.docx")
```

## Model comparison

Let's quickly look at the DIC for each model:

```{r dic}
data.frame(model=c("full","no spatial","only spatial","no random effects"),
           dic=c(output_all$dic$dic,
                 output_all_no_spde$dic$dic,
                 output_all_only_spde$dic$dic,
                 output_all_no_res$dic$dic),
           waic=c(output_all$waic$waic,
                  output_all_no_spde$waic$waic,
                  output_all_only_spde$waic$waic,
                  output_all_no_res$waic$waic)) %>% kable
```

## Variance decomposition

```{r var decomp}
## spatial model
rf <- inla.spde.result(inla = output_all,name="spatial.field",
                       spde=spde,do.trans=TRUE)

med_spde_var <- inla.emarginal(function(x) x,
                               rf$marginals.variance.nominal[[1]])
vil_var <- inla.emarginal(function(x) 1/x,
                          output_all$marginals.hyperpar$`Precision for village.index`)
hhl_var <- inla.emarginal(function(x) 1/x,
                          output_all$marginals.hyperpar$`Precision for hh.index`)
binom_var <- (pi ^ 2) / 3 

hhl_var / (vil_var + hhl_var + binom_var + med_spde_var)
vil_var / (vil_var + hhl_var + binom_var + med_spde_var)
med_spde_var / (vil_var + hhl_var + binom_var + med_spde_var) 
```

Leave-one-out predictions:

```{r loocv}
adj_rf_ests <- readRDS("generated_data/results-rf-365-youden.rds")$cell_adjusted_incidence %>% 
    group_by(community_cell, obs) %>%
    summarize(adjusted_incidence=mean(adjusted_reps))
dat_no_na <- serosurvey_dat %>% 
    left_join(adj_rf_ests) %>%
    group_by(community_cell) %>%
    summarise(n_tested = n(),
              adjusted_incidence = adjusted_incidence[1],
              n_pos_rf_cor = floor(adjusted_incidence[1] * n()),
              original_incidence = mean(pred_365),
              n_pos_rf = sum(pred_365),
              logpop = logpop[1],
              poverty = poverty[1],
              travel_time = travel_time[1],
              distance_to_water = distance_to_water[1],
              altitude = altitude[1],
              grid_easting = grid_easting[1],
              grid_northing = grid_northing[1],
              hhids = paste(hhid,collapse=";"))

## observation/prediction matrix
A_est_multi <- inla.spde.make.A(mesh=mesh,
                                loc=dat_no_na %>%
                                    select(grid_easting,grid_northing) %>%
                                    as.matrix)

## leave one grid-id out of the fitting and predict on it
## save just the mean quantiles for each
## will do with covariates
rc = NULL
for(gc in dat_no_na$community_cell){
    cat(".")
    
    tmp_dat = dat_no_na %>%
        mutate(n_pos_rf_cor = ifelse(community_cell == gc,NA,n_pos_rf_cor))
    
    tmp_mod_matrix = model.matrix(~logpop+distance_to_water,
                                  tmp_dat)[,-1]
    
    tmp_est_stack = inla.stack(
        data=list(y=tmp_dat[,'n_pos_rf_cor'] %>% unlist,
                  n=dat_no_na[,'n_tested'] %>% unlist), ## response
        A=list(A_est_multi,1), ## projector matrix
        effects=list(s_index,
                     data.frame(Intercept=rep(1,nrow(tmp_dat)),tmp_mod_matrix)),
        tag="tmp")
    
    all_covs_f <- y ~ -1 + Intercept + logpop + distance_to_water + f(spatial.field, model = spde)
    
    test =inla(all_covs_f,
               data=inla.stack.data(tmp_est_stack),
               family="binomial",
               verbose=FALSE,
               control.predictor=list(
                   A=inla.stack.A(tmp_est_stack),link=1,
                   compute=TRUE),
               control.compute=list(dic=FALSE,config=TRUE),
               Ntrials=tmp_dat$n_tested)
    
    summary_hold_out = test$summary.fitted.values[which(is.na(tmp_dat$n_pos_rf_cor)), c("mean", "sd","0.025quant","0.5quant","0.975quant")]
    summary_others = test$summary.fitted.values[which(!is.na(tmp_dat$n_pos_rf_cor)), c("mean", "sd","0.025quant","0.5quant","0.975quant")]
    
    rc = rbind(rc,
               data.frame(left_out_cell = gc,
                          summary_hold_out,
                          mean_others_mean = mean(summary_others$mean),
                          mean_others_median = mean(summary_others$`0.5quant`),
                          median_others_mean = median(summary_others$mean),
                          truth=dat_no_na %>% filter(community_cell==gc) %>% select(adjusted_incidence) %>% unlist))
}

## mean absolute error 

model_mae <- (rc$mean - rc$truth) %>% abs %>% mean 

naive_mae <- (rc$mean_others_mean - rc$truth) %>% abs %>% mean

## relative MAE
model_mae/naive_mae

obs_mae <- abs(rc$mean-rc$truth)
naive_obs_mae <-abs(rc$mean_others_mean-rc$truth)
sum(obs_mae<naive_obs_mae)

## bias 
model_bias <- (rc$mean - rc$truth) %>% mean

saveRDS(rc, "generated_data/loocv-results.rds")
```


From this we see that we do an OK job at predicting with a pearsons
correlation of `r cor(rc$mean,rc$truth)` ,  a mean
absolute error of `r (rc$mean - rc$truth) %>% abs %>% mean` and a bias
of `r (rc$mean - rc$truth) %>% mean`.

```{r session}
sessionInfo()
```
